\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-11-07 parts-example.tex
examples++
update computation times
phrase obsolète

This section aims at giving several applications of our work in order to
understand its results and range of applications.
First, \pref{ssec:phage-lambda} gives a detailed application of our IG inference method
by studying parts of a model of the phage lambda immunity control.
% the functioning of our method
% and the implementation of the software developed for this work.
% First, \pref{ssec:phage-lambda} aims at giving a detailed example of the application of our method
% on parts of a model of the phage lambda immunity control.
%We then explain the use of the implementation and usage of the software developed for this work:
Then, \pref{ssec:appli} gives a practical application of our results on a biological model
of epithelial growth factor receptor taken from the literature.
Finally, \pref{ssec:cpu} gives data related to the results and computation times of our software
when applied to several large biological models.

@@

\begin{table}[ht]
\begin{center}
  \begin{tabular}{r|c|c|c|c|c}
    \textbf{Model} & $\mathbf{|\Gamma|}$ & $\mathbf{|\PHs \setminus \Gamma|}$ & \textbf{$\Delta t$ IG} & \textbf{$\Delta t$ K} & $\mathbf{|K|}$
\\\hline\hline
    EGF receptor \cite{Sahin09} & $20$ & $22$ & <1s & <1s & 192
\\\hline
    T cell receptor \cite{Klamt06} & $40$ & $14$ & <1s & <1s & 143
\\\hline
    T cell receptor \cite{SaezRodriguez2007} & $94$ & $39$ & 10s & --- & $2.1\cdot10^{9}$
\\\hline
    EGF receptor \cite{Samaga2009} & $104$ & $89$ & 3min 20s & --- & $4.2\cdot10^{6}$
  \end{tabular}
\end{center}
\caption{%
  Computation times and several pieces of information related to the IG and parametrization inferences of four biological models.
  The second column gives the number of components of each model and
  the third column gives the number of cooperative sorts used to model joint actions.
  The fourth (resp.~fifth) column gives the computation times of the IG inference (resp.~the parametrization inference).
  The last column gives the number of parameters in each model.
  Due to the too high number of parameters, parametrization inference could not be performed on the $94$ and $104$ component models.
  }
\label{tb:computation}
\end{table}

>>>>

\modMF{%
This section aims at giving several applications of our work in order to
understand its results and range of applications.
First, \pref{ssec:phage-lambda} gives a detailed application of our IG inference method
by studying parts of a model of the phage lambda immunity control.
}%
% the functioning of our method
% and the implementation of the software developed for this work.
% First, \pref{ssec:phage-lambda} aims at giving a detailed example of the application of our method
% on parts of a model of the phage lambda immunity control.
%We then explain the use of the implementation and usage of the software developed for this work:
Then, \pref{ssec:appli} gives a practical application of our results on a biological model
of epithelial growth factor receptor taken from the literature.
Finally, \pref{ssec:cpu} gives data related to the results and computation times of our software
when applied to several large biological models.

@@

\begin{table}[ht]
\begin{center}
  \begin{tabular}{r|c|c|c|c|c}
    \textbf{Model} & $\mathbf{|\Gamma|}$ & $\mathbf{|\PHs \setminus \Gamma|}$ & \textbf{$\Delta t$ IG} & \textbf{$\Delta t$ K} & $\mathbf{|K|}$
\\\hline\hline
    EGF receptor \cite{Sahin09} & $20$ & $22$ & <1s & <1s & 192
\\\hline
    T cell receptor \cite{Klamt06} & $40$ & $14$ & <1s & <1s & 143
\\\hline
    T cell receptor \cite{SaezRodriguez2007} & $94$ & $39$ & 100s & <1s & 578
\\\hline
    EGF receptor \cite{Samaga2009} & $104$ & $89$ & 200s & 2.5s & 27496
  \end{tabular}
\end{center}
\caption{%
  Computation times and several pieces of information related to the IG and parametrization inferences of four biological models.
  The second column gives the number of components of each model and
  the third column gives the number of cooperative sorts used to model joint actions.
  The fourth (resp.~fifth) column gives the computation times of the IG inference (resp.~the parametrization inference).
  The last column gives the number of parameters in each model.
  }
\label{tb:computation}
\end{table}
